\documentclass{article}
\title{\textbf{COEP CAMPUS}}
\author{Rohit Bhaurao Torkad}
\date{11/11/2022}


\begin{document}
\maketitle
\pagenumbering{gobble}
\newpage
\pagenumbering{roman}
\tableofcontents
\newpage
\pagenumbering{arabic}
\section{North Campus}

	\subsection{Computer and IT dept.}
	\paragraph{The Department was established in 1992, with Computer Engineering and Information Technology branches. It is one of the youngest departments at the institute. The undergraduate course in Computer Engineering was started in 1992 and Information Technology in 2000. Both these courses have an intake of 60 students each} 
.
\subparagraph{Vision is To be one of the best in the country by developing globally competent engineers, motivated entrepreneurs, prospective researchers, and aspiring academicians}.
\newpage

	\subsection{Mechanical dept.}
	\paragraph{ The Department of Mechanical Engineering was established in the year 1912. At present, the department offers Graduate, Post Graduate and Doctoral degree courses. The department has recently started the Post Graduate Diploma in Electric Mobility}.
\newpage
	\subsection{ENTC dept.}
	\paragraph{ Established in 1948, the department has always remained on the forefront in producing quality engineers who have brought great laurels to the institute, society and nation at large}.
	\subparagraph{The department has a tradition of attracting the topmost merit students at UG from across the state and is becoming a favored destination of PG students after the IITs}.	
	\newpage
	\subsection{Instrumentation dept.}
\paragraph{ The Department of Instrumentation and Control started in the year 1965 with the support of the Central Government. The Undergraduate and Postgraduate programmes offered by the department are accredited by the National Board of Accreditation (NBA)}k.
\subparagraph{ The department boasts qualified, experienced and dedicated faculty to impart fundamental and applied knowledge in the field of Industrial Automation, Process Systems Engineering, Instrumentation Systems Engineering and Biomedical Instrumentation}.
\newpage
	\subsection{Other buildings}
	\subsubsection{BHAU Ecell}
	\subsubsection{Academic complex}
	\subsubsection{Boat club}
\newpage
\section{South Campus}

	\subsection{Civil Dept.}
	 \paragraph{ The department of Civil Engineering established in 1854 has the distinction of being the oldest department in the institute. It has set up a great tradition of producing distinguished engineers such as Bharat Ratna late Sir. M. Visvesvarayya who through his countless works is synonymous with Civil engineering}. \subparagraph{ Even after completing its sesquicentennial anniversary, the department has kept updating to well-equipped laboratories and research}.
	 \newpage
	\subsection{Production Dept.}
	\paragraph{ Established in the year 1994, the Production Engineering department of CoEP with its team of dedicated, qualified and experienced faculty, offers a sound programme at both UG and PG levels}. \subparagraph{ The department aims at providing a valuable resource not only to the industries but also the society through excellence in technical education and research}.
	\newpage 
	\subsection{Electrical Dept.}
	\paragraph{ It gives me immense pleasure in welcoming, on behalf of the Department of Electrical Engineering at College of Engineering Pune. The Department established in 1932, running UG program since 1932 and PG programs in Power Systems and Control Systems since 1952}.
	\newpage
	\subsection{Metallurgy Dept.}
	\paragraph{ Established in 1948, the Department of Metallurgy and Materials Science of COEP is a unique establishment in and around western Maharashtra in educating students as Metallurgical and Materials Engineers}. \subparagraph{ Day by day, the demand of this skilled human resource in the industry is rising sharply due to the globalization of Indian economy. The department strives hard in fulfilling these requirements}.
	\newpage
	\subsection{Other buildings}
	\subsubsection{Main Building}
	\subsubsection{Mathematics Dept.}
\subsubsection{Meta canteen}
\subsubsection{Geology Dept.}

	



\end{document}
